Diffusion-limited mixing by incompressible flows

### 2017-10-05 nonlinearity/manuscript.tex
finished revisoins on discussion

@@

@@

% Figures \ref{fig:enstrophy_norms} and \ref{fig:energy_norms} show the evolution the  $H^{-1}$,  $L^{2}$, and $H^{1}$ norms for different values of finite $Pe$.

\section{Discussion}
\label{sec:discussion}
The local-in-time optimisation results suggest that there is a limiting length scale and rate. The bounds derived, under the $L^{\infty}$ constrained flow assumption, did not result in proving either of these observations. However, they did definitively rule out the possibility of perfect mixing in finite time in either constraint. We believe these bounds could be drastically improved. We surmise that the deficiencies in these bounds is due to not fully exploiting the incompressibility condition. It remains to be shown that $\liminf_{t\rightarrow \infty} \lambda (t)\geq C\lambda_{\Gamma}$ where C is constant dependent on domain and initial condition under an enstrophy constrained flow. A similar problem remains open for the fixed energy case.  If these statements are shown, then many of the results demonstrated here numerically will hold more generally.

In future work, we would like to consider the optimal control problem coined global-in-time optimisation which tries to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate. This may lead to flows that are able to extend to even smaller length scales. This global-in-time optimisation has been explored in the work of \cite{Miles2017a} within the context of the shell model. The authors showed that global-in-time and local-in-time optimisation appeared to give similar mixing rates.

>>>>

%%%
%%%
%%% THEORY
%%%
%%%

@@

%%%
%%%
%%% RESULTS
%%%
%%%

@@

%%%
%%%
%%% DISCUSSION 
%%%
%%%

\section{Discussion}
\label{sec:discussion}
The local-in-time optimisation results suggest that there is a limiting length scale for passive tracer mixing whenever flows are optimised to decrease the mix-norm. The bounds derived under the $L^{\infty}$ constrained flow assumption did not result in proving either of these observations, but they did definitively rule out the possibility of perfect mixing in finite time for either constraint. These bounds could be drastically improved: we surmise that the deficiencies in these analyses may be due to not fully exploiting the incompressibility condition in the estimates. It remains to be shown that $\liminf_{t\rightarrow \infty} \lambda (t)\geq C\lambda_{\Gamma}$ where C is constant dependent on domain and initial condition under an enstrophy constrained flow. A similar problem remains open for the fixed energy case.  If these statements can be shown, then many of the results demonstrated here computationally will hold more generally.

In future work, we would like to consider the optimal control problem with finite-time optimisation to minimise the filamentation width at the end time rather than instantaneously attempting to minimise its decay rate. This might lead to flows that are able to extend to even smaller length scales. Finite-time optimisation was explored in \cite{Miles2017a} in the context of the shell model where it was found that global-in-time and local-in-time optimisation appeared to give similar mixing rates. Fore the shell model, however, the analysis was consistent with computation. In the PDE case the gap between analysis and computation remains to be closed.

%%%
%%%
%%% CONCLUSION
%%%
%%%
